When is Finding Little Graphs \\ Inside Big Graphs Hard?

### 2015-10-20 data-presentation-talk/talk.tex
Talk

        \node [anchor=west, xshift=0.2cm] at (current page.west |- logo.west) {
            \begin{minipage}{0.65\paperwidth}\raggedright
                {\usebeamerfont{title}\usebeamercolor[white]{}\inserttitle}\\[0.1cm]
                {\usebeamerfont{author}\usebeamercolor[white]{}\insertauthor}
            \end{minipage}
        };
    \end{tikzpicture}
}

@@

\title[When is Finding Little Graphs Inside Big Graphs Hard?]{When is Finding Little Graphs \\ Inside Big Graphs Hard?}
\author[Ciaran McCreesh and Patrick Prosser]{\textbf{Ciaran McCreesh} and Patrick Prosser}

@@

\begin{frame}{A Phase Transition}
\end{frame}

\begin{frame}{2D Phase Transitions}
\end{frame}

\begin{frame}{3D Phase Transitions}
\end{frame}

\begin{frame}{Reductions}
\end{frame}

>>>>

        \node [anchor=west, xshift=0.2cm] at (current page.west |- logo.west) {
            \begin{minipage}{0.65\paperwidth}\raggedright
                {\usebeamerfont{title}\usebeamercolor[white]{}\inserttitle}\\[0.1cm]
                {\usebeamerfont{author}\usebeamercolor[white]{}\scriptsize\insertauthor}
            \end{minipage}
        };
    \end{tikzpicture}
}

@@

\title[When is Finding Little Graphs Inside Big Graphs Hard?]{When is Finding Little Graphs \\ Inside Big Graphs Hard?}
\author[Ciaran McCreesh, Patrick Prosser and James Trimble]{\textbf{Ciaran McCreesh}, Patrick Prosser and James Trimble}

@@

\begin{frame}[plain,t]{A Phase Transition}

    \only<1>{
        \input{gen-graph-phase-1}
    }

    \only<2>{
        \input{gen-graph-phase-2}
    }

    \only<3>{
        \input{gen-graph-phase-3}
    }

\begin{frame}{This Looks Familiar\ldots}
    \centering
    \includegraphics*[keepaspectratio=true,scale=0.25]{sat.jpg}

    \par\flushleft
    Understanding the Empirical Hardness of NP-Complete Problems. Kevin Leyton-Brown, Holger H.
    Hoos, Frank Hutter, Lin Xu.  Communications of the ACM, Vol. 57 No. 5, Pages 98-107
\end{frame}

\begin{frame}{2D Phase Transitions}

    \only<1>{
        \input{gen-graph-2d-1}
    }

    \only<2>{
        \input{gen-graph-2d-2}
    }

    \only<3>{
        \input{gen-graph-2d-3}
    }

\begin{frame}[plain,t]{3D Phase Transitions?}

    \only<1>{
        \input{gen-graph-3d-1}
    }

    \only<2>{
        \input{gen-graph-3d-2}
    }

\begin{frame}[t,plain]{What About Induced?}

    \only<1>{
        \input{gen-graph-induced-2d-1}
    }

    \only<2>{
        \input{gen-graph-induced-2d-2}
    }

    \only<3>{
        \input{gen-graph-induced-2d-3}
    }

    \only<4>{
        \input{gen-graph-induced-2d-4}
    }

    \only<5>{
        \input{gen-graph-induced-2d-5}
    }

    \only<6>{
        \input{gen-graph-induced-3d-1}
    }

    \only<7>{
        \input{gen-graph-induced-3d-2}
    }

\begin{frame}{Other Solvers?}

    \only<1>{
        \input{gen-graph-alt-1}
    }

    \only<2>{
        \input{gen-graph-alt-2}
    }

    \only<3>{
        \input{gen-graph-alt-3}
    }

\begin{frame}{Reductions}

    \only<1>{
        \input{gen-graph-red-1}
    }

    \only<2>{
        \input{gen-graph-red-2}
    }

    \only<3>{
        \input{gen-graph-red-3}
    }

    \only<4>{
        \input{gen-graph-red-4}
    }

    \only<5>{
        \input{gen-graph-red-5}
    }

\begin{frame}{Why the Weird Shape?}

    \only<1>{
        \input{gen-graph-shape-1}
    }

    \only<2>{
        \input{gen-graph-shape-2}
    }

    \only<3>{
        \input{gen-graph-shape-3}
    }

    \only<4>{
        \input{gen-graph-shape-4}
    }

    \only<5>{
        \input{gen-graph-shape-5}
    }
